Counterexamples in Mathematical Relations

### 2024-12-04 Relations/CounterExamples.tex
ARS-stuff
fixed counterexample 3
ARSwork
created notes.tex to merge various scattered bullet points

\documentclass{article}
\usepackage{tikz-cd}
\usepackage{amsmath}
\usepackage{mathrsfs}

\usetikzlibrary{positioning,shapes.geometric,fit}

@@

\end{center}
Counterexample to:
\begin{itemize}
    \item WCR $\to$ CR
    \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
\end{itemize}

@@

\subsection{Counterexample 3}
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (fi) at (3, 0) {$f_i$};
      \node (fi+1) at (4, 0) {$f_{i+1}$};
      \node (dots) at (2, 0) {$...$};
      \node (dots2) at (5, 0) {$...$};

@@

      % Draw the arrows between the nodes inside and outside the region f
      \draw[->>] (fi) -- (a);
      \draw[->>] (fi+1) -- (a);
      \draw[->>] (dots2) -- (a);
      \draw[->>] (y) -- (fi);
  \end{tikzpicture}
\end{center}
Counterexample to: 
\begin{itemize}
  \item RP-$\to$RP
  \item RP-$\land$WCR$\to$RP
\end{itemize}
\subsection{ARS in Agda}
Important counterexamples:
\begin{enumerate}
  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
  Counterexample to:
  \begin{itemize}
      \item WCR and WN implies CR.
  \end{itemize}
  \item Loop $a \to a$.
  Counterexample to:
  \begin{itemize}
    \item $\omega$-bounded and RP implies SN
    \item $\omega$-bounded and RP implies WN
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
  \begin{itemize}
    \item $WN$
    \item $\omega$-bounded
    \item $WCR \to WN$
    \item $CR \to WN$
    \item $CR, CP \to WN$
    \item $CR, CP \to \omega$-bounded
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.
  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
  $a_n \to a_0$, for each $n$.
  \item The combination of the last two.
  Counterexample to
  \begin{itemize}
    \item RP
  \end{itemize}
  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
  Counterexample to:
  \begin{itemize}
    \item $WN\to WCR$
    \item $WN \to SN$
  \end{itemize}
  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
\end{enumerate}

>>>>

\documentclass{article}

\input{macros}

@@

\end{center}
Counterexample to:
\begin{itemize}
    \item WCR $\to$ CR
    \item WCR and WN $\to$ CR
    \item WCR and WN $\to$ SN
    \item \mbox{WCR R $\to$ $\forall$ a b $\to$ is R -NF b $\to$ (R *) a b $\to$ $\forall$ c $\to$ (R *) a c $\to$ (R *) c b}
    \item IOW, WCR $\to$ WNFP
\end{itemize}

@@

\subsection{Counterexample 3} \sacomment{This counterexample doesn't work. Keeping it as a useful reminder.}
\begin{center}
  \begin{tikzpicture}
      % Define the nodes inside the region f
      \node (f0) at (0, 0) {$f_0$};
      \node (f1) at (1, 0) {$f_1$};
      \node (fi) at (3, 0) {$f_i$};
      \node (fi+1) at (4, 0) {$f_{i+1}$};
      \node (dots) at (2, 0) {$...$};
      \node (dots2) at (5, 0) {$...$};

@@

          % Draw the arrows between the nodes inside and outside the region f
          \draw[->>] (fi) to [bend right=15] (a);
          \draw[->>] (a) to [bend right=15] (fi);
          \draw[->>] (fi+1) -- (a);
          \draw[->>] (dots2) -- (a);
          \draw[->>] (fi) -- (y);   
      \end{tikzpicture}
    \end{center}
    Counterexample to:
    \begin{itemize}
      \item ***** DOES NOT WORK ******
      \item RP-$\to$RP 
      \item RP-$\land$WCR$\to$RP \textcolor{red}{NO< NEEDS A NEW CE}
\end{itemize}

\subsection{Other questions}
\begin{enumerate}
  \item If WCR holds, is WN$\downarrow\subseteq$WN ?
  \item Same question for next bullet in 2.2
  \item Same for bullet 3 in 2.2 (but pointwise!)
  \item Do RP- $\land$ WCR imply RP?
\end{enumerate}
\subsection{ARS in Agda}
Important counterexamples:
\begin{enumerate}
  \item $a,b,c,d$ with sinks $a$ and $d$ and a 2-cycle between $b$ and $c$.
  Counterexample to:
  \begin{itemize}
      \item WCR and WN implies CR.
  \end{itemize}
  \item Loop $a \to a$.
  Counterexample to:
  \begin{itemize}
    \item $\omega$-bounded and RP implies SN
    \item $\omega$-bounded and RP implies WN
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$. Falsifies:
  \begin{itemize}
    \item $WN$
    \item $\omega$-bounded
    \item RP $\to$ $\omega$-bounded
    \item $WCR \to WN$
    \item $CR \to WN$
    \item $CR, CP \to WN$
    \item $CR, CP \to \omega$-bounded
  \end{itemize}
  \item Infinite sequence $a_0 \to a_1 \to \cdots$ with a colimit $a_\infty$,
  with each $a_n \to a_\infty$ and $a_\infty$ a normal form.

  Counterexample to:
  \begin{itemize}
    \item WN $\to$ SN
    \item WN, CR $\to$ SN
    \item WN, CR, $\omega$-bounded $\to$ SN
  \end{itemize}

  \item Infinite sequence $a_0 \to a_1 \to \cdots$, together with links
  $a_n \to a_0$, for each $n$.
  \item The combination of the last two.
  Counterexample to
  \begin{itemize}
    \item RP
  \end{itemize}
  \item An ``infinite haircomb''. Infinite sequence $a_0 \to a_1 \to \cdots$, together with
  a disjoint, discrete set $b_0, b_1, \dots$, and links $a_n \to b_n$.
  Counterexample to:
  \begin{itemize}
    \item $WN\to WCR$
    \item $WN\to \omega-bounded$
    \item $WN \to SN$
    \item $WN,RP \to SN$
  \end{itemize}
  \item A variation of the above with backlinks $a_n \to a_0$ for all $n$.
\end{enumerate}

\section{Taken from other files and needs sorting into the above}
\sacomment{Check the tex file for the notes below which have been commented out.}
% -- Move to counterexamples; delete
%   -- Not provable: n <- x -> z
%   -- WN∧UN→CRelem : ∀ x → is R -WN x → is R -UN x → is R -CR x
%   -- WN∧UN→CRelem x x∈WN x∈UN  = Newmans-Lemma.CR→CRelem R (ii ({! x∈WN  !} , {!   !})) x -- Can we do this or am I being too bullheaded in comparing x∈UN and UN etc?

### 2024-12-04 Relations/notes.tex
Theorem 1.2.3 progress
report: counterexamples fleshed out. implications progress

@@

\section{Todo}
\subsection*{Week starting 11th November}
\begin{enumerate}
  \item In the report, give a classical proof that the $Inc$ Property
  implies that no $R$-increasing sequence is bounded.

>>>>

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\quad\ding{51}}%
\newcommand{\xmark}{\quad\ding{55}}%

\newcommand{\thra}{\twoheadrightarrow}
\newcommand{\thla}{\twoheadleftarrow}
\newcommand{\thlra}{{\thla\!\!\thra}}

@@

\subsection*{November 21}

Four local ``normal form properties'':
\begin{enumerate}
  \item $WNFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \tto b) \to (b \tto n)$
    "$a$ all reducts of $a$ reduce to $a$'s normal form, if it exists``
  \item $NFP(a) : \forall n \in NF. (a \tto n) \to \forall b. (a \thlra b) \to (b \tto n)$
    "$a$ all converta of $a$ reduce to $a$'s normal form, if it exists``
  \item $WUN(a) : \forall n m \in NF. (a \tto n) \to (a \tto m) \to n \equiv m$
    "$a$ is reducible to at most one normal form"
  \item $UN(a) : \forall n m \in NF. (a \thlra n) \to (a \thlra m) \to n \equiv m$
    "$a$ is convertible to at most one normal form''
\end{enumerate}

\section{Todo}

Look at Exercise 1.3.22

\subsection*{Week starting 11th November}
\begin{enumerate}
  \item[\cmark] In the report, give a classical proof that the $Inc$ Property
  implies that no $R$-increasing sequence is bounded.
